---
title: "R Markdown Presentation & Plotly"
author: "Maciej Gielnik"
date: "23 02 2022"
output:
  ioslides_presentation: default
  slidy_presentation: default
---
knitr::opts_chunk$set()

## R Markdown

This is an Assignment 2: R Markdown Presentation & Plotly for Developing Data 
Products course by John Hopkins University on Coursera. The goal of this assignment is to:

1. Create a web page presentation using R Markdown.
2. Web page presentation must contain a plot created with plotly.
3. Assignment should be hosted on GitHub Pages, RPubs, or NeoCities.

## Plot created with plotly


```{r, echo = FALSE, include=FALSE}
library(ggplot2)
library(plotly)
library(bio3d)

dcdfile <- read.dcd("apo_v2_dcd.dcd")
pdbfile <- read.pdb("apo_v2_input.pdb")


ca.inds <- atom.select(pdbfile, elety="CA")

xyz <- fit.xyz(fixed=pdbfile$xyz, mobile=dcdfile,
               fixed.inds=ca.inds$xyz,
               mobile.inds=ca.inds$xyz)


rd <- rmsd(xyz[1,ca.inds$xyz], xyz[,ca.inds$xyz])
rd_smooth <- lowess(rd)
ln <- c(1:101)
rd_df<- as.data.frame(cbind(ln, rd, rd_smooth$y))
```

```{r, include=FALSE}
my_plot <- plot_ly(rd_df, x = ~ln, y = ~rd, type = "scatter", mode = "lines", 
                   name = "RMSD")
my_plot <- my_plot %>% layout(xaxis = list(title = "time (ns)"), yaxis = list(title = "RMSD (A)"))
my_plot <- my_plot %>% add_trace( y = ~V3, mode ="lines", name = "RMSD smoothed")
```
Plot of a root-mean-square deviation (RMSD) of atomic positions for one of the proteins from my calsses 
(blue), and smoothed RMSD (orange).
```{r plot, echo = FALSE}
my_plot
```
## Thank you!